Generalized Tractability

### 2023-03-30 GeneralizedTractability_230310.tex
Updates from Overleaf

\subsection{Notation and fundamental definitions}
Let $T$ be a tractability function defined as follows,
\[
T :(0,\infty) \times \mathbb{N} \times [0,\infty)^s \rightarrow [1,\infty),
\]
A tractability function is a simple function that provides an upper bound on the computational complexity of a problem
A problem is $T$-tractable with parameter $\vp$ iff there exists a positive constant $C_{\vp}$ such that
\begin{equation} \label{eq:tract_def}
	\comp(\varepsilon,d) \le C_{\vp}\, T(\varepsilon^{-1},d,\vp) \qquad \forall \varepsilon >0, \ d \in \mathbb{N}.
\end{equation}
A problem is \emph{strongly}
$T$-tractable with parameter $\vp$ iff the complexity is independent of the dimension, that is, there exists a positive constant $C_{\vp}$ such that
\begin{equation} \label{eq:strong_tract_def}
	\comp(\varepsilon,d) \le C_{\vp}\, T(\varepsilon^{-1},1,\vp) \qquad \forall \varepsilon >0 , \ d \in \mathbb{N}.
\end{equation}
In this article we allow $\vp$ to be a scalar or vector as the situation requires.

Note that the tractability function is bounded below away from zero even as $\varepsilon \to \infty$, so that the information based complexity is not expected to vanish under arbitrarily loose error requirements.  For this definition of tractability to make sense we assume that
\begin{subequations} \label{eq:Tconditions}
\begin{equation}
	T \text{ is non-decreasing in all variables}
\end{equation}
which implies that the problem does not become easier by decreasing the tolerance, $\varepsilon$, or increasing the dimension, $d$. Since there are an infinite number of positive eigenvalues, it also make sense to assume that
\begin{equation}
	\lim_{\varepsilon \to 0} T(\varepsilon^{-1},d,\vp) = \infty \qquad \forall d \in \naturals, \ \vp \in [0,\infty)^s.
\end{equation}
Since $T(\cdot,d,\vp)$ is non-decreasing, we may define the following limit:
\begin{equation}
	T(0,d,\vp):=\lim_{\varepsilon\to\infty}T(\varepsilon^{-1},d,\vp).
\end{equation}
There is a technical assumption required for our analysis.  There exists a $K_{\vp,\tau}$ depending on $\vp$ and $\tau$, but  independent of $\varepsilon$ and $d$, such that
\begin{equation} \label{eq:ptauassume}
	[T(\varepsilon^{-1},d,\vp)]^\tau \le K_{\vp,\tau} T(\varepsilon^{-1},d,\tau \vp),   \quad \forall \varepsilon \in (0,\infty), \ d \in \naturals, \ \vp\in[0,\infty)^s, \ \tau\in (1,\infty).
\end{equation}
\end{subequations}

If \eqref{eq:tract_def} holds for some $\vp$, it clearly holds for larger, $\vp$.  We are often interested in the optimal or smallest $\vp$ for which \eqref{eq:tract_def} holds.  Define the closures of the sets of parameters for which our (strong) tractability conditions hold:
\begin{equation*}
	\cp_{\textup{trct}} : = \{\vp^* : \eqref{eq:tract_def} \text{ holds }\forall \vp \in (\vp^*,\boldsymbol{\infty})\}, \qquad
	\cp_{\textup{strct}} : = \{\vp^* : \eqref{eq:strong_tract_def} \text{ holds }\forall \vp \in (\vp^*,\boldsymbol{\infty})\}.
\end{equation*}
The  set of optimal parameters is defined as all of those parameters satisfying the (strong) tractability conditions that are not greater than or equal to others:
\begin{gather}
	\label{eq:Poptdef}
	\mathcal{P}_{\textup{opt}} : = \{\vp^* \in \cp_{\textup{trct}} :  \vp* \notin [\vp^\dagger,\boldsymbol{\infty}) \ \forall \vp^\dagger \in  \cp_{\textup{trct}} \setminus \{\vp^*\} \}, \\
	\label{eq:Psoptdef}
	\mathcal{P}_{\textup{sopt}} : = \{\vp^* \in \cp_{\textup{strct}} :  \vp* \notin [\vp^\dagger,\boldsymbol{\infty}) \ \forall \vp^\dagger \in  \cp_{\textup{strct}} \setminus \{\vp^*\} \}.
\end{gather}

@@

In the sections below we prove necessary and sufficient conditions on tractability as generally defined in \eqref{eq:tract_def} and \eqref{eq:strong_tract_def}.  These conditions  that involve the boundedness of sums defined in terms of $\{T(\lambda_{i,d}^{-1},\cdot, \cdot)\}_{i=1}^\infty$.  In practice, it may be easier to verify whether or not these conditions hold than to deal with \eqref{eq:comp_def} directly.

@@

\begin{theorem}\label{thm_main_strong_tract2}
A problem is strongly $T$-tractable iff there exists $\vp \in [\vzero, \boldsymbol{\infty})$ and an integer $L_{\vp} > 0$ such that
\begin{equation} \label{eq:strong_tractiff3}
     S(\vp):=\sup_{d \in \naturals} \sum_{i = L_{\vp}}^\infty \frac{1}{T(\lambda_{i,d}^{-1},1,\vp)} < \infty.
\end{equation}
If \eqref{eq:strong_tractiff3} holds for some $\vp$, let  $\widetilde{\cp}_{\textup{strct}} : = \{\vp^* : \eqref{eq:strong_tractiff3} \text{ holds }\forall \vp \in (\vp^*,\boldsymbol{\infty})\}$.  Then $\cp_{\textup{strct}} = \widetilde{\cp}_{\textup{strct}}$, and the set of optimal strong tractability parameters is
\[
	\cp_{\textup{sopt}} =
	\{\vp^* \in \widetilde{\cp}_{\textup{strct}} :  \vp* \notin [\vp^\dagger,\boldsymbol{\infty}) \ \forall \vp^\dagger \in  \widetilde{\cp}_{\textup{strct}} \setminus \{\vp^*\} \}.
\]
\end{theorem}

\begin{proof}
\textbf{Sufficient condition:}\newline
We make the first part of the argument in some generality so that it can be reused in the proof of Theorem \ref{thm_main_tract2} for tractability.  Given that $T$ is increasing in its arguments, we have the following equivalent expression for the complexity:
    \begin{equation} \label{eq:comp_equiv}
    \comp(\varepsilon, d) = \min \{n \in \natzero : \lambda_{n+1, d} \le \varepsilon\} = \min \biggl\{n \in \natzero : \frac{1}{T(\lambda_{n+1,d}^{-1},d',\vp)}\le \frac{1}{T(\varepsilon^{-1},d',\vp) }\biggr\},
\end{equation}
for any $d' \in \naturals$.

Also since the $\lambda_{i,d}$ are non-increasing in $i$, it follows that the $T(\lambda_{i,d}^{-1},d',\vp)$ are non-decreasing in $i$. In particular, for all $n\in \mathbb{N}$, we have
\begin{align*}
    \lambda_{n+1,d} \le \lambda_{n,d} \le \cdots \le \lambda_{1,d}
    & \implies \frac{1}{T(\lambda_{n+1, d}^{-1},d',\vp)} \le \frac{1}{T(\lambda_{n, d}^{-1},d',\vp)} \le \cdots \le \frac{1}{T(\lambda_{1, d}^{-1},d',\vp)} \\
    & \implies \frac{1}{T(\lambda_{n+1, d}^{-1},d',\vp) }
    \le \frac 1n \sum_{i=1}^n  \frac{1}{T(\lambda_{i, d}^{-1},d',\vp) }
    \le \frac 1n \sum_{i=1}^\infty  \frac{1}{T(\lambda_{i, d}^{-1},d',\vp)}.
\end{align*}
Thus, we can conclude from the previous line that
\begin{multline*}
    n \ge T(\varepsilon^{-1},d',\vp) \sum_{i=1}^\infty \frac{1}{T(\lambda_{i, d}^{-1},d',\vp)} \\
   \implies   \frac{1}{T(\lambda_{n+1, d}^{-1},d',\vp)} \le
   \frac 1n \sum_{i=1}^\infty \frac{1}{T(\lambda_{i, d}^{-1},d',\vp) } \le \frac{1}{T(\varepsilon^{-1},d',\vp)} \qquad \forall \varepsilon > 0, \ d,d' \in \naturals.
\end{multline*}
This last inequality together with \eqref{eq:comp_equiv} implies an upper bound on the complexity: of
\begin{equation} \label{eq:compUP}
	\comp(\varepsilon,d)
	\le 1 + T(\varepsilon^{-1},d',\vp) \sum_{i=1}^\infty \frac{1}{T(\lambda_{i, d}^{-1},d',\vp)} \qquad \forall \varepsilon > 0, \ d, d' \in \naturals
\end{equation}

Now we take this upper bound further, specializing to the case of $d'=1$:
\begin{align*}
       \comp(\varepsilon,d)
       & = 1 + T(\varepsilon^{-1},1, \vp) \Biggl [ \sum_{i=1}^{L_{\vp}-1} \frac{1}{T(\lambda_{i, d}^{-1},1,\vp)}
       + \underbrace{\sum_{i=L(p)}^\infty \frac{1}{T(\lambda_{i, d}^{-1},1,\vp)}}_{\le S(p) <\infty\ \text{by \eqref{eq:strong_tractiff3}} }\Biggr] \\
       & \le 1+ T(\varepsilon^{-1},1,\vp) \underbrace{\left[\frac{(L(p)-1)}{T(\lambda_{\max}^{-1},1,\vp)} + S(\vp)\right]}_{=:C_1(\vp)}\\
       & = 1+ T(\varepsilon^{-1},1,\vp) C_1 (p)\\
       &\le C_{\vp} T(\varepsilon^{-1},1,\vp),
\end{align*}
for some suitably chosen $C_{\vp}>0$. This means that we have strong $T$-tractability via \eqref{eq:strong_tract_def}, and verifies the sufficiency of \eqref{eq:strong_tractiff3}.

@@

For $\varepsilon$ taking on all positive values, $j(\varepsilon,\vp)$ takes on all values greater than or equal to $L(\vp)$, so
\[
j\le C_{\vp}\, T(\varepsilon^{-1},1,\vp)+1 \le C_{\vp} T(\lambda_{j,d}^{-1},1,\vp)+1, \qquad \forall j \ge L(\vp).
\]
This implies via our technical assumption \eqref{eq:ptauassume} that
\begin{equation*}
 K_{\vp,\tau}\,T (\lambda_{j,d}^{-1},1,\tau \vp) \ge
 [T(\lambda_{j,d}^{-1},1, \vp)]^\tau
 \ge
  \left[\frac{(j-1)}{C_{\vp}}\right]^\tau \qquad \forall j \ge L(\vp)
\end{equation*}
Summing both sides of the inequality yields it follows that
\begin{equation*}
\sup_{d\in\naturals} \sum_{j=j (\infty,\vp)}^\infty \frac{1}{T (\lambda_{j,d}^{-1},1, \tau \vp)}
\le K_{\vp,\tau}\, C_{\vp}^\tau
\sum_{j=j (\infty,\vp)}^\infty \frac{1}{(j-1)^\tau} \le
K_{\vp,\tau}\, C_{\vp}^\tau\, \zeta (\tau) < \infty,
\end{equation*}
where $\zeta$ denotes the Riemann zeta function.
This yields \eqref{eq:strong_tractiff3} with $\vp$ replaced by $\vp' = \tau \vp$ and $L_{\vp'} = j (\infty,\vp)$, and so we see the necessity of $\eqref{eq:strong_tractiff3}$.

@@

@@

\begin{theorem}\label{thm_main_tract2}
A problem is $T$-tractable iff there exist $\vp\ge \vzero$ and a constant $L(\vp) > 0$ such that
\begin{equation} \label{eq:tractiff4}
     S(\vp):=\sup_{d \in \naturals}
     \sum_{i = \lceil L(\vp)\, T(0,d,\vp) \rceil}^\infty \frac{1}{T(\lambda^{-1}_{i,d},d,\vp)}< \infty.
\end{equation}
If \eqref{eq:tractiff4} holds for some $\vp$, let  $\widetilde{\cp}_{\textup{trct}} : = \{\vp^* : \eqref{eq:tractiff4} \text{ holds }\forall \vp \in (\vp^*,\boldsymbol{\infty})\}$.  Then $\cp_{\textup{trct}} = \widetilde{\cp}_{\textup{trct}}$, and the set of optimal strong tractability parameters is
\[
\cp_{\textup{opt}} =
\{\vp^* \in \widetilde{\cp}_{\textup{trct}} :  \vp* \notin [\vp^\dagger,\boldsymbol{\infty}) \ \forall \vp^\dagger \in  \widetilde{\cp}_{\textup{trct}} \setminus \{\vp^*\} \}.
\]\end{theorem}

@@

Let $J(\vp,d): = \lceil L(\vp)\, T(0,d,\vp)\rceil$.  Then this upper bound on the complexity can be further bounded above by
\begin{align*}
       \comp(\varepsilon,d)
       & = 1 + T(\varepsilon^{-1},d,\vp) \Biggl [ \sum_{i=1}^{J(\vp,d) -1} \frac{1}{T(\lambda_{i, d}^{-1},d,\vp)}
       + \underbrace{\sum_{i=J(\vp,d)}^\infty \frac{1}{T(\lambda_{i, d}^{-1},d,\vp)}}_{\le S(\vp) \text{ by \eqref{eq:tractiff4}}} \Biggr ] \\
       & \le 1+ T(\varepsilon^{-1},d,\vp)\left[ \frac{J(\vp,d)-1}{T(\lambda_{\max}^{-1},d,\vp)} + S(\vp)\right]
        \\
       & \le 1+ T(\varepsilon^{-1},d,\vp)\left[L(\vp)\, T(0,d,\vp) + S(\vp)\right] \qquad \text{since } T(\lambda_{\max}^{-1},d,\vp) \ge 1\\
       & \le 1+L(\vp)\,T(\varepsilon^{-1},d,\vp) T(0,d,\vp) + S(\vp)\, T(\varepsilon^{-1},d,\vp)\\
       & \le 1+L(\vp)\,T(\varepsilon^{-1},d,\vp) T(\varepsilon^{-1},d,\vp) + S(\vp)\, T(\varepsilon^{-1},d,\vp)\\
       & \le 1+L(\vp)\,K_{\vp,2} T(\varepsilon^{-1},d,2\vp)  + S(\vp)\, T(\varepsilon^{-1},d,\vp)  \qquad \text{by \eqref{eq:ptauassume}}\\
       & \le C_{2}(2\vp) \,T(\varepsilon^{-1},d,2\vp)
\end{align*}
for some suitably chosen $C_{2}(2\vp)>0$. It follows that we have $T$-tractability, which shows sufficiency of \eqref{eq:tractiff4}. \\

>>>>

\subsection{Notation and fundamental definitions}
Let $T$ be a tractability function defined as follows,
\[
T :(0,\infty) \times \mathbb{N} \times [0,\infty)^s \rightarrow [1,\infty),
\]
A tractability function is a function of simple form that provides an upper bound on the computational complexity of a problem.
A problem is defined as $T$-tractable with parameter $\vp$ iff there exists a positive constant $C_{\vp}$ such that
\begin{equation} \label{eq:tract_def}
	\comp(\varepsilon,d) \le C_{\vp}\, T(\varepsilon^{-1},d,\vp) \qquad \forall \varepsilon >0, \ d \in \mathbb{N}.
\end{equation}
A problem is \emph{strongly}
$T$-tractable with parameter $\vp$ iff the complexity is independent of the dimension of the problem, that is, there exists a positive constant $C_{\vp}$ such that
\begin{equation} \label{eq:strong_tract_def}
	\comp(\varepsilon,d) \le C_{\vp}\, T(\varepsilon^{-1},1,\vp) \qquad \forall \varepsilon >0 , \ d \in \mathbb{N}.
\end{equation}
In this article we allow $\vp$ to be a scalar or vector as the situation requires.

Note that the tractability function is bounded below away from zero even as $\varepsilon \to \infty$, so that the information based complexity is not expected to vanish under arbitrarily loose error requirements.  For this definition of tractability to make sense we assume that
\begin{subequations} \label{eq:Tconditions}
\begin{equation}
	T \text{ is non-decreasing in all variables}
\end{equation}
which implies that the problem does not become easier by decreasing the tolerance, $\varepsilon$, or increasing the dimension, $d$. Furthermore, increasing $\vp$ does not decrease $T(\cdot, \cdot, \vp)$.  Since there are an infinite number of positive eigenvalues, it also make sense to assume that
\begin{equation}
	\lim_{\varepsilon \to 0} T(\varepsilon^{-1},d,\vp) = \infty \qquad \forall d \in \naturals, \ \vp \in [0,\infty)^s.
\end{equation}
Since $T(\cdot,d,\vp)$ is non-decreasing, we may define the following limit:
\begin{equation}
	T(0,d,\vp):=\lim_{\varepsilon\to\infty}T(\varepsilon^{-1},d,\vp).
\end{equation}
Finally, there is a technical assumption required for our analysis.  There exists a $K_{\vp,\tau}$ depending on $\vp$ and $\tau$, but  independent of $\varepsilon$ and $d$, such that
\begin{equation} \label{eq:ptauassume}
	[T(\varepsilon^{-1},d,\vp)]^\tau \le K_{\vp,\tau} T(\varepsilon^{-1},d,\tau \vp),   \quad \forall \varepsilon \in (0,\infty), \ d \in \naturals, \ \vp\in[0,\infty)^s, \ \tau\in (1,\infty).
\end{equation}
\end{subequations}

If \eqref{eq:tract_def} holds for some $\vp$, it clearly holds for larger, $\vp$.  We are often interested in the optimal or smallest $\vp$ for which \eqref{eq:tract_def} holds.  Define the closures of the sets of parameters for which our (strong) tractability conditions hold:
\begin{equation*}
	\cp_{\textup{trct}} : = \{\vp^* : \eqref{eq:tract_def} \text{ holds }\forall \vp \in (\vp^*,\boldsymbol{\infty})\}, \qquad
	\cp_{\textup{strct}} : = \{\vp^* : \eqref{eq:strong_tract_def} \text{ holds }\forall \vp \in (\vp^*,\boldsymbol{\infty})\}.
\end{equation*}
The  set of optimal parameters is defined as all of those parameters satisfying the (strong) tractability conditions that are not greater than or equal to others:
\begin{gather}
	\label{eq:Poptdef}
	\mathcal{P}_{\textup{opt}} : = \{\vp^* \in \cp_{\textup{trct}} :  \vp^* \notin [\vp^\dagger,\boldsymbol{\infty}) \ \forall \vp^\dagger \in  \cp_{\textup{trct}} \setminus \{\vp^*\} \}, \\
	\label{eq:Psoptdef}
	\mathcal{P}_{\textup{sopt}} : = \{\vp^* \in \cp_{\textup{strct}} :  \vp^* \notin [\vp^\dagger,\boldsymbol{\infty}) \ \forall \vp^\dagger \in  \cp_{\textup{strct}} \setminus \{\vp^*\} \}.
\end{gather}

@@

In the sections below we prove necessary and sufficient conditions on tractability as generally defined in \eqref{eq:tract_def} and \eqref{eq:strong_tract_def}.  These conditions involve the boundedness of sums defined in terms of $\{T(\lambda_{i,d}^{-1},\cdot, \cdot)\}_{i=1}^\infty$.  In practice, it may be easier to verify whether or not these conditions hold than to verify \eqref{eq:comp_def} directly.

@@

\begin{theorem}\label{thm_main_strong_tract2}
A problem is strongly $T$-tractable iff there exists $\vp \in [\vzero, \boldsymbol{\infty})$ and an integer $L_{\vp} > 0$ such that
\begin{equation} \label{eq:strong_tractiff3}
     S_{\vp}:=\sup_{d \in \naturals} \sum_{i = L_{\vp}}^\infty \frac{1}{T(\lambda_{i,d}^{-1},1,\vp)} < \infty.
\end{equation}
If \eqref{eq:strong_tractiff3} holds for some $\vp$, let  $\widetilde{\cp}_{\textup{strct}} : = \{\vp^* : \eqref{eq:strong_tractiff3} \text{ holds }\forall \vp \in (\vp^*,\boldsymbol{\infty})\}$.  Then $\cp_{\textup{strct}} = \widetilde{\cp}_{\textup{strct}}$, and the set of optimal strong tractability parameters is
\[
	\cp_{\textup{sopt}} =
	\{\vp^* \in \widetilde{\cp}_{\textup{strct}} :  \vp* \notin [\vp^\dagger,\boldsymbol{\infty}) \ \forall \vp^\dagger \in  \widetilde{\cp}_{\textup{strct}} \setminus \{\vp^*\} \}.
\]
\end{theorem}

\begin{proof}
\textbf{Sufficient condition:}\newline
We make the first part of the argument in some generality so that it can be reused in the proof of Theorem \ref{thm_main_tract2} for tractability.

Since the $\lambda_{i,d}$ are non-increasing in $i$, it follows that the $T(\lambda_{i,d}^{-1},d',\vp)$ are non-decreasing in $i$. In particular, for all $n\in \mathbb{N}$, we have
\begin{align*}
    \lambda_{n+1,d} \le \lambda_{n,d} \le \cdots \le \lambda_{1,d}
    & \implies \frac{1}{T(\lambda_{n+1, d}^{-1},d',\vp)} \le \frac{1}{T(\lambda_{n, d}^{-1},d',\vp)} \le \cdots \le \frac{1}{T(\lambda_{1, d}^{-1},d',\vp)} \\
    & \implies \frac{1}{T(\lambda_{n+1, d}^{-1},d',\vp) }
    \le \frac 1n \sum_{i=1}^n  \frac{1}{T(\lambda_{i, d}^{-1},d',\vp) }
    \le \frac 1n \sum_{i=1}^\infty  \frac{1}{T(\lambda_{i, d}^{-1},d',\vp)}.
\end{align*}
Thus, we can conclude from the previous line that
\begin{multline} \label{eq:implicate_a}
    n \ge T(\varepsilon^{-1},d',\vp) \sum_{i=1}^\infty \frac{1}{T(\lambda_{i, d}^{-1},d',\vp)} \\
   \implies   \frac{1}{T(\lambda_{n+1, d}^{-1},d',\vp)} \le
   \frac 1n \sum_{i=1}^\infty \frac{1}{T(\lambda_{i, d}^{-1},d',\vp) } \le \frac{1}{T(\varepsilon^{-1},d',\vp)} \qquad \forall \varepsilon > 0, \ d,d' \in \naturals.
\end{multline}

Moreover, given that $T$ is increasing in its arguments, we have the following equivalent expression for the complexity via \eqref{eq:comp_def}:
    \begin{equation*} %\label{eq:comp_equiv}
    \comp(\varepsilon, d) = \min \{n \in \natzero : \lambda_{n+1, d} \le \varepsilon\} = \min \biggl\{n \in \natzero : \frac{1}{T(\lambda_{n+1,d}^{-1},d',\vp)}\le \frac{1}{T(\varepsilon^{-1},d',\vp) }\biggr\},
\end{equation*}
for any $d' \in \naturals$.  Combining this expression for the complexity with the implication in \eqref{eq:implicate_a}, we can conclude from the previous line that
\begin{equation} \label{eq:compUP}
	\comp(\varepsilon,d)
	\le 1 + T(\varepsilon^{-1},d',\vp) \sum_{i=1}^\infty \frac{1}{T(\lambda_{i, d}^{-1},d',\vp)} \qquad \forall \varepsilon > 0, \ d, d' \in \naturals
\end{equation}

Now we take this upper bound further, specializing to the case of $d'=1$:
\begin{align*}
       \comp(\varepsilon,d)
       & = 1 + T(\varepsilon^{-1},1, \vp) \Biggl [ \sum_{i=1}^{L_{\vp}-1} \frac{1}{T(\lambda_{i, d}^{-1},1,\vp)}
       + \underbrace{\sum_{i=L_{\vp}}^\infty \frac{1}{T(\lambda_{i, d}^{-1},1,\vp)}}_{\le S_{\vp} <\infty\ \text{by \eqref{eq:strong_tractiff3}} }\Biggr] \\
       & \le 1+ T(\varepsilon^{-1},1,\vp) \underbrace{\left[\frac{(L(p)-1)}{T(\lambda_{\max}^{-1},1,\vp)} + S_{\vp}\right]}_{=:C_{1,\vp}}\\
       & = 1+ T(\varepsilon^{-1},1,\vp) C_{1,\vp}\\
       & \le \underbrace{2 C_{1,\vp}}_{\text{since } T(\varepsilon^{-1},1,\vp) \ge 1} T(\varepsilon^{-1},1,\vp)
       = \underbrace{C_{\vp}}_{:=2 C_{1,\vp}}T(\varepsilon^{-1},1,\vp).
\end{align*}
This means that we have strong $T$-tractability via \eqref{eq:strong_tract_def}, and verifies the sufficiency of \eqref{eq:strong_tractiff3}.

@@

For $\varepsilon$ taking on all positive values, $j(\varepsilon,\vp)$ takes on all values greater than or equal to $j(\infty,\vp)$, so
\[
j\le C_{\vp} T(\lambda_{j,d}^{-1},1,\vp)+1, \qquad \forall j \ge j(\infty,\vp).
\]
This implies via our technical assumption \eqref{eq:ptauassume} that
\begin{equation*}
 K_{\vp,\tau}\,T (\lambda_{j,d}^{-1},1,\tau \vp) \ge
 [T(\lambda_{j,d}^{-1},1, \vp)]^\tau
 \ge
  \left[\frac{(j-1)}{C_{\vp}}\right]^\tau \qquad \forall j \ge j(\infty,\vp)
\end{equation*}
Summing both sides of the inequality yields it follows that
\begin{equation*}
\sup_{d\in\naturals} \sum_{j=j (\infty,\vp)}^\infty \frac{1}{T (\lambda_{j,d}^{-1},1, \tau \vp)}
\le K_{\vp,\tau}\, C_{\vp}^\tau
\sum_{j=j (\infty,\vp)}^\infty \frac{1}{(j-1)^\tau} \le
K_{\vp,\tau}\, C_{\vp}^\tau\, \zeta (\tau) < \infty,
\end{equation*}
where $\zeta$ denotes the Riemann zeta function.
This yields \eqref{eq:strong_tractiff3} with $\vp$ replaced by $\vp' = \tau \vp$ and $L_{\vp'} = j (\infty,\vp)$, and so we see the necessity of $\eqref{eq:strong_tractiff3}$.

@@

\subsection{Tractability} \label{sec:tractability}

@@

\begin{theorem}\label{thm_main_tract2}
A problem is $T$-tractable iff there exist $\vp\ge \vzero$ and a constant $L(\vp) > 0$ such that
\begin{equation} \label{eq:tractiff4}
     S_{\vp}:=\sup_{d \in \naturals}
     \sum_{i = \lceil L(\vp)\, T(0,d,\vp) \rceil}^\infty \frac{1}{T(\lambda^{-1}_{i,d},d,\vp)}< \infty.
\end{equation}
If \eqref{eq:tractiff4} holds for some $\vp$, let  $\widetilde{\cp}_{\textup{trct}} : = \{\vp^* : \eqref{eq:tractiff4} \text{ holds }\forall \vp \in (\vp^*,\boldsymbol{\infty})\}$.  Then $\cp_{\textup{trct}} = \widetilde{\cp}_{\textup{trct}}$, and the set of optimal strong tractability parameters is
\[
\cp_{\textup{opt}} =
\{\vp^* \in \widetilde{\cp}_{\textup{trct}} :  \vp* \notin [\vp^\dagger,\boldsymbol{\infty}) \ \forall \vp^\dagger \in  \widetilde{\cp}_{\textup{trct}} \setminus \{\vp^*\} \}.
\]\end{theorem}

@@

Let $J(\vp,d): = \lceil L(\vp)\, T(0,d,\vp)\rceil$.  Then this upper bound on the complexity can be further bounded above by
\begin{align*}
       \comp(\varepsilon,d)
       & = 1 + T(\varepsilon^{-1},d,\vp) \Biggl [ \sum_{i=1}^{J(\vp,d) -1} \frac{1}{T(\lambda_{i, d}^{-1},d,\vp)}
       + \underbrace{\sum_{i=J(\vp,d)}^\infty \frac{1}{T(\lambda_{i, d}^{-1},d,\vp)}}_{\le S_{\vp} \text{ by \eqref{eq:tractiff4}}} \Biggr ] \\
       & \le 1+ T(\varepsilon^{-1},d,\vp)\left[ \frac{J(\vp,d)-1}{T(\lambda_{\max}^{-1},d,\vp)} + S_{\vp}\right]
        \\
       & \le 1+ T(\varepsilon^{-1},d,\vp)\left[L(\vp)\, T(0,d,\vp) + S_{\vp}\right] \qquad \text{since } T(\lambda_{\max}^{-1},d,\vp) \ge 1\\
       & \le 1+L(\vp)\,T(\varepsilon^{-1},d,\vp) T(0,d,\vp) + S_{\vp}\, T(\varepsilon^{-1},d,\vp)\\
       & \le 1+L(\vp)\,T(\varepsilon^{-1},d,\vp) T(\varepsilon^{-1},d,\vp) + S_{\vp}\, T(\varepsilon^{-1},d,\vp)\\
       & \le 1+L(\vp)\,K_{\vp,2} T(\varepsilon^{-1},d,2\vp)  + S_{\vp}\, T(\varepsilon^{-1},d,\vp)  \qquad \text{by \eqref{eq:ptauassume}}\\
       & \le C_{2}(2\vp) \,T(\varepsilon^{-1},d,2\vp)
\end{align*}
for some suitably chosen $C_{2}(2\vp)>0$. It follows that we have $T$-tractability, which shows sufficiency of \eqref{eq:tractiff4}. \\
